---
title: "Comments_Carey"
author: "Fazhir"
date: "3/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Loading packages
Library(Package.name) allows me to use an already installed package or one that comes along with another installed package e.g ggplot with installed Tidyverse. I included package installation for those that you hadn't installed. 
```{r}
#install.packages("janitor")
#install.packages("tidyverse")
#install.packages("plyr") 
#install.packages("reshape2")
```
#Dimensions of yopur files
I would use "dim(file.name)" instead of just reading it out. Just in case my files are bigger than the ones we are having. It helps avoid opening very large files in your console as they might take alot of time and space.
```{r}
#dim(fang) ##Also works
#dim(snp)
```
#Transposition
The t() is a good command but works better if you create an intermediate file to incorporate the title of interest and eliminate one you do not want. In this case, the file will have the first column as SNP_ID such that it doesn't consider the first column as if it were row.names. I tried running this as part of your chunk and it made it really awesome.
```{r}
#intermediate_maize <- maize[-(1:3)]
#trans_maize <- t(intermediate_maize) %>% as.data.frame() %>% rownames_to_column(., var = "SNP_ID")
#view(trans_maize)
```
#Creating the files
This could have worked well on your computer since the directory you listed was on it. It has however failed to create them on mine. What I did though was to create an empty folder in on my PC and then use one snippet to create all the files at once. 
```{r}
#dir.create('./Maize_files')
#chr_maize <- filter(maize_quest, Chromosome != "multiple" & Chromosome != "unknown")
for (i in 1:length(unique(chr_maize$Chromosome))) {
  chrom <- chr_maize %>% filter(Chromosome == i) %>% arrange(Position)
  write.table (chrom, file = paste("./Maize_files/Maize_A", i, sep = "_"), quote = FALSE)
}
```
#Plotting 
Since he had requested that we plot him graphs as PDF, I decided to run this snippet with your file and it worked well too. It involves directing the plotted graph to a file (Plot) and then telling it to plot the file and save it as a PDF.
```{r}
ggplot(bind1, aes(x=Chromosome, fill= Species, color= Species)) + geom_bar(bins=10, position = "dodge")
Plot <- ggplot(bind1, aes(x=Chromosome, fill= Species, color= Species)) + 
  geom_bar() +
  scale_x_continuous(breaks = 1:10) + # bcs x=as.double(Chromosome), breaks by default don't match chrom number
pdf("Plot.pdf")
print(Plot)
dev.off()
```

